---
title             : "DoPL"
shorttitle        : "Title"

author: 
  - name          : "Ithurburn, Andrew"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "7 George Square, Edinburgh, EH8 9JZ"
    email         : "a.ithurburn@sms.ed.ac.uk"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Pedersen, Julie"
    affiliation   : "1"
  - name          : "Moore, Adam"
    affiliation   : "1"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "The University of Edinburgh"
  

authornote: 
 

abstract:
  
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         :  "591"

bibliography      : ["cite_examples.bib", "r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
mainfont: "Times New Roman"
always_allow_html: true
header-includes:
  - \raggedbottom

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---


```{r setup, include = FALSE}
library("papaja")
library(ggplot2)
library(sjPlot)
library(RColorBrewer)
library(tidyr)
library(grid)  
library(gtable)  
library(DiagrammeR)
library(lubridate)
library(DT)
library(kableExtra)
library(svgPanZoom)
library(knitr)
library(ggmcmc)
library(ggridges)
library(rstan)
library(insight)
library(shiny)
library(gridExtra)
library(ggpubr)
library(gghighlight)
library(ggtext)
library(readr)
library(ggcorrplot)
library(ggprism)
library(brms)
library(parameters)
r_refs("cite_examples.bib")
experiment_1_Dataset <- read.csv("experiment_1_data.csv")
load(".rData")
rCitations <- cite_r(file = "r-references.bib", footnote = F)
demo_table <- read_csv("demo_table.csv", 
    col_names = FALSE)
theme_set(theme_apa(base_size = 12))

time_df <- read.csv("DoPL_DOSPERT.csv")
time_df <- time_df[-1:-2,]
library(lubridate) 
average_completion <- median(as.numeric(time_df$Duration..in.seconds.)) 
stdv_DF <- sd(as.numeric(time_df$Duration..in.seconds.)) 
average_completion <- seconds_to_period(average_completion) 
stdv_DF <- seconds_to_period(stdv_DF)

```


# Introduction

Throughout political history tyrants and despots have influenced great power over large swaths of land and communities. One common thread amongst these individuals are how they wield their great power, often through dominant tactics such as threats and political subversions. Recent history has shown with individuals like Donald Trump, Jair Bolsonaro, and Rodrigo Duterte who display authoritarian traits often wield their power through fear and threats of violence. 

## Dominance, Leadership, and Prestige orientation

Research in power desire motives have focused on three sub-domains: dominance, leadership, and prestige [@suessenbach_dominance_2019]. Each of these thre different power motives are explanations as to different ways or methods that individuals in power sought power or were bestowed upon them. 

The dominance motive is one of the more researched methods and well depicted power motives. Individuals with a dominance orientation display the more primal of human behavior. These individuals will seek power through direct methods such as asserting one's dominance, control over resources, or physically assaulting someone [@johnson_dominance_2012; @winter_power_1993]. The method of attaining this power and status may not always be as direct as a physical confrontation. Use of nonverbal communication is often very common amongst humans such as body posture, facial expressions, and 

## Risk

## Domain Specific Risk-taking

## The present study

# Methods
Participants were a convenience sample of 111 individuals from Prolific Academic’s crowdsourcing platform (www.prolific.io). Prolific Academic is an online crowdsourcing service that provides participants access to studies hosted on third party websites. Participants were required to be 18 years of age or older and be able to read and understand English. Participants received £4.00, which is above the current minimum wage pro-rata in the United Kingdom, as compensation for completing the survey. The Psychology Research Ethics Committee at the University of Edinburgh approved all study procedures [ref: ####]. The present study was pre-registered along with a copy of anonymized data and copy of R code is available at (https://osf.io/s4j7y). 

## Materials

*Demographic Questionnaire*. In a demographic questionnaire administered prior to the main survey, participants were invited to respond to questions about their self-identified demographic characteristics such as gender, ethnicity, and ethnic origin. 

*Dominance, Prestige, and Leadership Orientation*. The 18-item Dominance, Prestige, and Leadership scale [DoPL; @suessenbach_dominance_2019], is used to measure dominance, prestige, and leadership orientation. Each question corresponds to one of the three domains. Each domain is scored across six unique items related to those domains (e.g., "I relish opportunities in which I can lead others" for leadership) rated on a scale from 0 (Strongly disagree) to 5 (Strongly agree). Internal consistency reliability for the current sample is $\alpha$ = `r psych::alpha(experiment_1_Dataset[,DoPLQuestions])$total$std.alpha`. 
	
*Domain Specific Risk-taking Scale* (DOSPERT; @weber_domain-specific_2002) is a scale assessing individuals' likelihood of engaging in risky behaviors within 5 domain specific risky situations: financial ("Gambling a week's income at a casino."), social ("Admitting that your tastes are different from those of your friends"), recreational ("Trying out bungeeing jumpng at least once"), health and safety ("Engaging in unprotected sex"), and ethical ("Cheating on an exam") situations. Each risky situation is then rated on a five-point Likert scale (1 being very unlikely and 5 being very likely). Two additional five-point Likert scales assess risk perception and expected benefits (1 being not at all risky and 5 being extremely risky; 1 being no benefits at all and 5 being great benefits) respectively. Example risky situations are “Admitting that your tastes are different from those of a friend” and “Drinking heavily at a social function.” Internal consistency reliability for the current samples for the 3 sub-domains are $\alpha$ = `r psych::alpha(experiment_1_Dataset[,riskQuestions], check.keys = TRUE)$total$std.alpha`, $\alpha$ = `r psych::alpha(experiment_1_Dataset[,riskPerceptionQuestions], check.keys = TRUE)$total$std.alpha`, $\alpha$ = `r psych::alpha(experiment_1_Dataset[,riskBenefitQuestions], check.keys = TRUE)$total$std.alpha` respectively. 

## Procedure
Participants were recruited via a study landing page on Prolific's website or via a direct e-mail to eligible participants (Prolific FAQ, 2018). The study landing page included a brief description of the study including any risks and benefits along with expected compensation for successful completion. Participants accepted participation in the experiment and were directed to the main survey (Qualtrics, Inc; Provo, UT) where they were shown a brief message on study consent. 

Once participants consented to participate in the experiment they answered a series of demographic questions. Once completed, participants completed the Dominance, Prestige, and Leadership Scale and the Domain Specific Risk-taking scale. The two scales were counterbalanced to account for order effects. After completion of the main survey, participants were shown a debriefing statement that briefly mentions the purpose of the experiment along with the contact information of the main researcher (AI). Participants were compensated £4.00 via Prolific Academic. 

## Data analysis
Demographic characteristics were analyzed using a multiple regression for continuous variables (age) and Chi-square tests for categorical variables (gender, race, ethnicity, ethnic origin, and education). Means and standard deviations were calculated for the relevant scales (i.e., DoPL and DOSPERT). All analyses were done using [@R-base] along with [@rStan] package.

*Note: discuss and explain the use of Bayesian Statistics

All relevant analyses were conducted in a Bayesian framework using the brms package [@brms-2021] along with the rstan package [@rStan]

# Results

One hundred and eleven individuals completed the main survey. Of these individuals, 111 completed all sections without incomplete data and were therefore retained in most data analyses. In later analyses to account for outliers two participants had to be excluded from the dataset. Table 1 shows the demographic information for the participants. Average completion time for participants was `r (average_completion)`(*SD* = `r (stdv_DF)`). 


## Preregistered Analyses

We first investigated DoPL orientation on general risk preference (Figure 1). General risk preference was anecdotally explained by dominance orientation, participant gender, and participant age (see table 2). 

*Demographic and DoPL*

All participants completed the dominance, leadership, and prestige scale (@suessenbach_dominance_2019). Empirically, men have generally been more dominance oriented in their behavior (citation). Following the literature, men tended to be more dominant oriented than women. The marginal posterior distribution of each parameter is summarized in Table #. Interestingly, older individuals tended to be more dominant oriented than younger individuals. 

## Domain Specific Risk-Taking



## Interactions

When investigating dominance, prestige, and leadership motivations with domain specific risk-taking findings supported the common expectations in the literature. Table 5 shows the interactions with like CI values. Dominance overall explained the relationship of DoPL orientation and preference, specifically for ethical, financial, social, health and safety, and recreational preference. Participant age and gender also appeared to affect recreational preference. 

Following these findings we investigated the effect of DoPL on general risk preference and found that dominance overall affected risk preference along with gender and age of the participant (Table 5). 
# Discussion

## Limitations

## Future Implications

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

\newpage

# Figures and Tables

```{r}

apa_table(
 demo_table, stub_indents = list("Age" = c(2:3), "Gender" = c(4:6), "Ethnicity" = c(7:15), "Education" = c(16:21)), col.names = c("Variables", "")
)

```

```{r}
dopl_domains_df <- experiment_1_Dataset
dopl_domains_df <- dopl_domains_df %>%
  gather(key = DoPL_domain, value = value, "dominanceSum":"leadershipSum")
dopl_domains_df <- dopl_domains_df[, -2:-179]
dopl_domains_ggplot <- ggplot(dopl_domains_df, aes(DoPL_domain, value, fill = DoPL_domain)) + 
  geom_violin() 
dopl_domains_ggplot + scale_fill_brewer(name = "DoPL Domain", palette = "Dark2", labels = c("Dominance", "Leadership", "Prestige")) + scale_shape_prism() + scale_y_continuous(limits = c(0, 40), guide = "prism_minor") + scale_x_discrete(name = "DoPL Domain", guide = "prism_bracket", labels = c("Dominance", "Leadership", "Prestige"))
```

```{r}

age_dom_df <- subset(experiment_1_Dataset, Age!= "")
gender_experiment_data <- subset(experiment_1_Dataset, Gender != "2")
gender_and_dominance <- ggplot(gender_experiment_data, aes(x = as.factor(Gender), y = dominanceSum, group = Gender, fill = as.factor(Gender))) + 
  geom_boxplot()  
gender_and_dominance  + scale_shape_prism() + scale_y_continuous(limits = c(0, 30), guide = "prism_offset", name = "Dominance") + scale_x_discrete(labels = c("Male", "Female"), guide = "prism_bracket", name = "Gender") + labs(fill = "Gender") + scale_fill_manual(name = "Gender", labels = c("Male", "Female"), values = c("#A6CEE3", "#FF7F00"))

gender_and_prestige <- ggplot(gender_experiment_data, aes(x = as.factor(Gender), y = prestigeSum, group = Gender, fill = as.factor(Gender))) + 
  geom_boxplot()  
gender_and_prestige  + scale_shape_prism() + scale_y_continuous(limits = c(0, 30), guide = "prism_offset", name = "Prestige") + scale_x_discrete(labels = c("Male", "Female"), guide = "prism_bracket", name = "Gender") + scale_fill_manual(name = "Gender", labels = c("Male", "Female"), values = c("#A6CEE3", "#FF7F00"))

gender_and_leadership <- ggplot(gender_experiment_data, aes(x = as.factor(Gender), y = leadershipSum, group = Gender, fill = as.factor(Gender))) + 
  geom_boxplot()  
gender_and_leadership  + scale_shape_prism() + scale_y_continuous(limits = c(0, 30), guide = "prism_offset", name = "Leadership") + scale_x_discrete(labels = c("Male", "Female"), guide = "prism_bracket", name = "Gender")+ scale_fill_manual(name = "Gender", labels = c("Male", "Female"), values = c("#A6CEE3", "#FF7F00"))
```
```{r}
hdi_table <- m1_hdi[sign(m1_hdi$CI_low) == sign(m1_hdi$CI_high),
            c('Parameter', 'CI','CI_low', 'CI_high')]
apa_table(hdi_table)
```

```{r}
fixed_effects_table <- fixef(m1)
apa_table(fixed_effects_table)
```

```{r}
 m3_hdi <- hdi(m3, effects = "fixed", component = "conditional", ci = .95)
apa_table(m3_hdi[sign(m3_hdi$CI_low) == sign(m3_hdi$CI_high),
      c('Parameter', 'CI','CI_low', 'CI_high')])
```

